Large squeezing in multicomponent trapped Bose-Einstein condensates

### 2012-11-21 large_number_squeezing_with_atoms.tex
spatial

As our goal is to describe the number squeezing possibilities of a two component BEC, we begin by considering a simplified version of the problem, consisting of a two-mode system, with the modes corresponding to the two states of the condensate. In the full problem, each of the components will include many spacial modes; our two mode system makes the assumption that only one of these spacial modes is relevant for each of the condensate's components.

@@

If we allow the problem to have multiple spacial modes, there are a number of effects that prevent us from achieving the levels of number squeezing predicted by the zero-dimensional, two-mode analytic model. In this section we consider the two problems caused by the fact that the density in a spatially multimode problem will not be constant.

>>>>

As our goal is to describe the number squeezing possibilities of a two component BEC, we begin by considering a simplified version of the problem, consisting of a two-mode system, with the modes corresponding to the two states of the condensate. In the full problem, each of the components will include many spatial modes; our two mode system makes the assumption that only one of these spatial modes is relevant for each of the condensate's components.

@@

If we allow the problem to have multiple spatial modes, there are a number of effects that prevent us from achieving the levels of number squeezing predicted by the zero-dimensional, two-mode analytic model. In this section we consider the two problems caused by the fact that the density in a spatially multimode problem will not be constant.
